\begin{thebibliography}{-----------}
\bibitem[CHE-2007]{CHEN} S. Chen, A. Ailamaki, et al.: {\textit{Improving hash join performance through prefetching}}. In: ACM Transactions on Database Systems, Vol. 32 Issue 3 August 2007, Artikel 17 New York, USA

\bibitem[GAR-2007]{GARCIA} P. Garcia, H. F. Korth: {\textit{Pipelined Hash-Join on Multithreaded Architectures}}. In: Pipelined Hash-Join on Multithreaded Architectures (DaMoN 07), Juni 15, 2007, Beijing, China, Seite 2

\bibitem[GOL-2005]{GOLD} B. Gold, A. Ailamaki, et al.: {\textit{Accelerating database operators using a network processor}}. In: Proceedings of the 1st international workshop on Data management on new hardware (DaMoN '05). ACM, New York, NY, USA, , Artikel 1 

\bibitem[GOV-2006]{GOVINDARAJU} N. Govindaraju, J. Gray, et al.: {\textit{GPUTeraSort: high performance graphics co-processor sorting for large database management}}. In: Proceedings of the 2006 ACM SIGMOD international conference on Management of data (SIGMOD '06)

\bibitem[HE-2009]{HE} B. He, M. Lu, et al.: {\textit{Relational query coprocessing on graphics processors}}. In: ACM Transactions on Database Systems (TODS), Volume 34 Issue 4, December 2009, ACM New York, USA 

\bibitem[HUB-2009]{HUBER} F. Huber, J. Freytag: {\textit{Query Processing on Multi-Core Architectures}}. In: Grundlagen von Datenbanken, Vol. CS-02-09 Universität Rostock (2009) , p. 27-31.

\bibitem[INO-2007]{INOUE} H. INOUE, T. Moriyama, et al.: {\textit{AA-Sort: A New Parallel Sorting Algorithm for Multi-Core SIMD Processors}}. In: Proceedings of the 16th International Conference on Parallel Architecture and Compilation Techniques (PACT '07), IEEE Computer Society, Washington, DC, USA, 189-198.

\bibitem[LAC-1991]{LACEY} S. Lacey, R. Box: {\textit{A fast, easy sort}}. In: BYTE 16, Vol. 4, April 1991, S.315 ff.

\bibitem[LEE-2009]{LEE} R. Lee, X. Ding, et al.: {\textit{MCCDB: Minimizing Cache Conflicts in Multicore Processors for Databases}}. In: Proceedings of the VLDB Endowment, Vol. 2, Issue 1 (August 2009), S.373-384

\bibitem[PAN-2011]{PANKRATIUS} V. Pankratius, M. Heneka: {\textit{Parallel SQL Query Auto-Tuning on Multicore}}. In: Karlsruhe Reports in Informatics 2011-5, edited by Karlsruhe Institute of Technology, Faculty of Informatics, Februar 2011

\bibitem[RAS-2008]{RASHID} L. Rashid, W. Hassanein, et al.: {\textit{Exploiting multithreaded architectures to improve the hash join operation}}. In: Proceedings of the 9th workshop on MEmory performance: DEaling with Applications, systems and architecture (MEDEA '08), 2008

\bibitem[SAL-2011]{SALOMIE} T. Salomie, I. Subasu, et al.: {\textit{Database engines on multicores, why parallelize when you can distribute?}}. In: Proceedings of the sixth conference on Computer systems (EuroSys '11), 2011
 
\end{thebibliography}

Bingsheng He, Mian Lu, Ke Yang, Rui Fang, Naga K. Govindaraju, Qiong Luo, and Pedro V. Sander. 2009. Relational query coprocessing on graphics processors. ACM Trans. Database Syst. 34, 4, Article 21 (December 2009), 39 pages.